% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{moderncv}
\moderncvtheme[black]{classic}
% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}
% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}
% Makes resume-specific commands available.
\usepackage{resume}

\begin{document}  % begin the content of the document

% title on top of the document

%\maintitle{Zachary J. Rice}{}{Last update on \today}{}
%\newline
%\noindent{zricezrice9@gmail.com}\sbull
%\textsmaller217-714-5103

\firstname{Zachary J.}
\familyname{Rice}
\phone{217-714-5103}
\email{zricezrice@gmail.com}
\social[github][www.github.com/zricethezav]{github.com/zricethezav}
\social[linkedin][www.linkedin.com/in/zricethezav]{linkedin.com/in/zricethezav}
\begin{document}
\makecvtitle 

\section{Experience}
\headedsubsection
{\textbf{Software Engineer} -- Gannett, Urbana}
{May \apo18 -- present}
{\begin{itemize} % Description(s) of tasks/responsibilities
    \item {Manage  Gannett's CDN layer which is responsible for all 120+ properties Gannett owns, including USATODAY.com.}
    \item {Maintain Gannett's API Gateway via Apigee.}
    \item {Develop Go applications for internal customers (slackbots, management apis, automation tools, etc).}
    \item {Orchestrate migration of our apps to Helm/Kubernetes.}
    \item {Support the security team for internal audits using Gitleaks.}
    \item {Migrate our Jenkins CI from a scripted pipeline to a declarative pipeline.}
    \item {Engage with external vendors like CDN and API gateway providers.}
 \end{itemize}}
}


\headedsubsection
{\textbf{Software Engineer} -- Agrible, Champaign}
{October \apo15 -- May \apo18}
{\begin{itemize} % Description(s) of tasks/responsibilities
    \item {Developed Python code for our services hosted on AWS leveraging technologies like Kinesis, Firehose, Redshift, and Lambda.}
    \item {Developed internal tools for managing workflows and scheduling jobs.}
    \item {Participated in daily standups, sprint planning and intern management.}
 \end{itemize}}
}

\headedsubsection
{\textbf{Teaching Assistant} -- University of Illinios, Urbana}
{August \apo14 -- December \apo15}{\break{\emph{ECE 220, Computer Systems and Programming}}}
{\begin{itemize} % Description(s) of tasks/responsibilities
    \item {Taught lab sections twice a week and taught lectures when professor was absent.}
 \end{itemize}}
}

\headedsubsection
{\textbf{Systems Intern} -- State Farm Research and Development Center, Champaign}
{May \apo14 -- August \apo14}
{\begin{itemize} % Description(s) of tasks/responsibilities
    \item {Developed a computer vision project using OpenCV and Xbox Kinect to detect and track unsafe driving behaviors. This project was open sourced to a Kaggle competition, \emph{State Farm Distracted Driver Detection}, for a \$65,000 prize -- \url{https://www.kaggle.com/c/state-farm-distracted-driver-detection}.}
 \end{itemize}}
}


\headedsubsection
{\textbf{Accelerator Control Intern} -- Fermilab, Batavia}
{May \apo13 -- Aug \apo13}
{\begin{itemize} % Description(s) of tasks/responsibilities
    \item {Created a replacement for a legacy application that was used to manage thousands of hardware instruments throughout Fermilab's campus.}
 \end{itemize}}
}


\section{Education}

\headedsubsection
{\textbf{University of Illinois, Electrical and Computer Engineering}, Urbana, IL}
{August \apo13 -- December \apo15}{\break{\emph{Bachelor of Science in Computer Engineering}}}
{\begin{itemize} % Description(s) of tasks/responsibilities
    \item {Member of ACM-SIG Music and ACM-SIG Computer Human Interaction}
    \item {GPA: 3.11/4.0}
 \end{itemize}}
}

\headedsubsection
{\textbf{Parkland College}, Urbana, IL}
{December \apo12 -- May \apo13}{\break{\emph{Associate of Science in Electrical Engineering Sciences and Computer Science}}}
{\begin{itemize} % Description(s) of tasks/responsibilities
    \item {GPA: 3.61/4.0}
    \item {Awards: Dean's List, Walter H. Miller Scholarship, Heartland Bank Scholarship, UIUC's Employee Scholarship}
 \end{itemize}}
}



\section{Projects}
\headedsubsection
{\textbf{GitLeaks} -- \url{github.com/zricethezav/gitleaks}}
{}
{\begin{itemize} % Description(s) of tasks/responsibilities
    \item {Tool to search Git repos for leaked API keys and secrets using regex and entropy}
    \item {4.4k stars on Github}
    \item {Active community, 40 releases, and 26 contributors}
 \end{itemize}}
}

\headedsubsection
{\textbf{Others} -- \url{github.com/zricethezav}}
{}
{\begin{itemize} 
    \item {whatSpeed - Download and upload speed checker written in Go} 
    \item {h1domains - OSINT Python script to gather all in scope domains for hackerone bounties}
    \item {zachstalks - Python script to download Youtube audio then upload to The Internet Archive}
 \end{itemize}}
}


\section{Skills}
\inlineheadsection
{Languages: }{Go, C, Python, VCL, Bash, C++, Haskell, Java, x86, CUDA, PostgresSQL, Groovy, \LaTeX }
\inlineheadsection
{Technologies: }{Jenkins, Fastly, Apigee, GCP, AWS, Kubernetes, Helm, Docker, Django, Flask, Redis, Postgres, Elastic-Search, Celery, Heroku, Vagrant, Wireshark, BurpSuite, Selenium, Vim}



\end{document}

